An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: fix fix fix

A thorough explanation of the information stored in a metadata record follows. Table \ref{tab:metadataRecord} summarizes the information.

\begin{description}
  \item[Node IP:] The IP address of the node that the metadata record describes. This is used by peers who wish to back up a file on this node to directly contact the node.
  \item[Blacklisters:] The list of (peer ID, timestamp) pairs, where the peer IDs are the IDs of those who have determined that the node is \textit{unreliable} (see section \ref{sec:ChurnandDataMigration_DataExchange} for the definition of what makes a node unreliable) and the timestamp is the time when the ID was inserted. This information is used by peers who are considering using the node as a backup location in the future. If the node has too many blacklisters (greater than some number $n$), peers will decide against using that node, and move on to select another node. In order to prevent sybil attacks, where a malicious user has many identities and blacklists a node many times, the number of blacklisters should be a nontrivial amount and proportional to the size of the network. In order to prevent nodes from permanently being shut out from the network, entries in the blacklist are removed some set amount of time after they are inserted; this is accomplished via the aforementioned timestamp.
  \item[Backed Up Files:] The list of information on the files backed up by the peer that the metadata record describes. Each element in the list stores the following data: the file ID, the filesize, the list of replicant node IPs, and a timestamp indicating when each replicant node stored the file. The \textit{file ID} is a unique identifier for the file, and must be in the same address space as node IDs (as explained in section \ref{subsubsec:StructuredOverlayNetworks}). This information is used by peers looking to recover their data. After retrieving their own metadata record, peers will ask the corresponding replicant nodes to transfer the data for each file they wish to recover. The more replicant nodes that are online for a given file, the faster the recovery of the file (due to the BitTorrent protocol used in the data layer). The timestamp is not yet used, but is included because future revisions to the specification may need it (for example, for peers to check that the node's replica is up-to-date).
  \item[Stored Files:] The list of information on the files stored by the node that the metadata record describes. Each element in the list stores the following data: the file ID, the filesize, the peer backing up the file, and a timestamp indicating when the node stored the file. This information, in conjunction with the information in \textbf{Backed Up Files}, is used as part of the fairness mechanism, described in section \ref{sec:Fairness}.
\end{description}

>>>>

A metadata record stores the following information for each node in the system: (node IP, blacklisters, backed up files, stored files). A thorough explanation of the information stored in a metadata record follows. Table \ref{tab:metadataRecord} summarizes the information.

\begin{description}
  \item[Node IP:] The IP address of the node that the metadata record describes. This is used by peers who wish to back up a file on this node to directly contact it.
  \item[Blacklisters:] The list of (peer ID, timestamp) pairs, where the peer IDs are the IDs of those who have determined that the node is \textit{unreliable} (see section \ref{sec:ChurnandDataMigration_DataExchange} for the definition of what makes a node unreliable) and the timestamp is the time when the ID was inserted. This information is used by peers who are considering using the node as a backup location. If the node has too many blacklisters (greater than some number $n$), peers will decide against using that node, and move on to select another node. In order to prevent sybil attacks, where a malicious user has many identities and blacklists a node many times, $n$ should be a nontrivial amount and proportional to the size of the network. In order to prevent nodes from permanently being shut out from the network, entries in the blacklist are removed some set amount of time after they are inserted; this is accomplished via the aforementioned timestamp.
  \item[Backed Up Files:] The list of information on the files backed up by the peer that the metadata record describes. Each element in the list stores the following data: the \textit{file ID}, the filesize, the list of replication node IPs, and a timestamp indicating when each replication node stored the file. The file ID is a unique identifier for the file, and must be in the same address space as node IDs (as explained in section \ref{subsubsec:StructuredOverlayNetworks}). This information is used by peers looking to recover their data. After retrieving their own metadata record, peers will ask the corresponding replication nodes to transfer the data for each file they wish to recover. The more replication nodes that are online for a given file, the faster the recovery of the file (due to the BitTorrent protocol used in the data layer). The timestamp is not yet used, but is included because future revisions to the specification may need it (for example, for peers to check that the node's replica is up-to-date).
  \item[Stored Files:] The list of information on the files stored by the node that the metadata record describes. Each element in the list stores the following data: the file ID, the filesize, the peer backing up the file, and a timestamp indicating when the node stored the file. This information, in conjunction with the information in \textbf{Backed Up Files}, is used as part of the fairness mechanism, described in section \ref{sec:Fairness}.
\end{description}
